Natural Stories model analyses

### 2021-07-22 Analysis/models.Rmd
different attempts to get something reasonable for SPR

---
title: "Natural Stories model analyses"
output: html_document
---

@@

>>>>

---
title: "Natural Stories model analyses"
output: 
  html_document:
    toc: true
---

@@

#data=readRDS("spr_pre_brms.rds")
data=read_rds(here("Analysis/models/spr_pre_brms.rds"))

run_model_lmer <- function(model_spec,data){
  d <- data %>% filter(model==model_spec)
  m1 <- lmer(rt ~ surp_center * length_center + length_center * freq_center +
                  past_surp_center * past_length_center + past_length_center * past_freq_center + 
                 past2_surp_center * past2_length_center + past2_length_center * past2_freq_center + 
                  past3_surp_center * past3_length_center + past3_length_center * past3_freq_center + 
              (surp_center + length_center +  freq_center +
                  past_surp_center + past_length_center + past_freq_center ||subject)+(1|Word_ID),
            data=d) 
  m1
}

run_model_lmer("GRNN",data) %>% write_rds(here("Analysis/models/grnn_spr_lmer.rds"))
run_model_lmer("5-gram",data) %>% write_rds(here("Analysis/models/5-gram_spr_lmer.rds"))
run_model_lmer("TXL",data) %>% write_rds(here("Analysis/models/txl_spr_lmer.rds"))
run_model_lmer("GPT-2",data) %>% write_rds(here("Analysis/models/gpt_spr_lmer.rds"))

```
## Summaries of LMER 
These have some heirarchical effects
```{r}
read_rds(here("Analysis/models/grnn_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/5-gram_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/txl_spr_lmer.rds")) %>% summary()
read_rds(here("Analysis/models/gpt_spr_lmer.rds")) %>% summary()
